### 2010-05-26 doc/tech_doc/xrsl/xrsl-urls.tex
document new checksum functionality

Metadata service URLs also support metadata options which can be used
for register additional metadata attributes or query the service using
metadata attributes. These options are specified at the end of the LFN
and consist of name and value pairs separated by colons. The following
attributes are supported:

@@

Currently these metadata options are only supported for lfc:// URLs.

@@

$^2$This is a destination URL. The file will be copied to
\texttt{srm.domain.org} at the path \texttt{griddir/file1} and registered to the LFC
service at \texttt{lfc.domain.org} with the LFN \texttt{/user/file1}. The given GUID
and checksum attributes will be registered.

>>>>

URLs also support metadata options which can be used for registering
additional metadata attributes or querying the service using metadata
attributes. These options are specified at the end of the LFN and
consist of name and value pairs separated by colons. The following
attributes are supported:

@@

The checksum attributes may also be used to validate files that were
uploaded to remote storage.

@@

$^2$This is a destination URL. The file will be copied to
\texttt{srm.domain.org} at the path \texttt{griddir/file1} and registered to the LFC
service at \texttt{lfc.domain.org} with the
LFN \texttt{/user/file1}. The checksum will be compared to what is
reported by the SRM service after the transfer. The given GUID and
checksum attributes will also be registered in the LFC.
